A quantitative framework for investigating the reliability of empirical network construction

### 2019-01-16 manuscript/reply_to_reviewers.tex

		\end{refquote}

		\textbf{R:} We believe that this comment stems from a lack of clarity about the goal of our model. It is not designed to separate the three levels of uncertainty or introduce parameters at particular levels. The only inputs are a prior distribution, which could refer to any level of uncertainty applicable to the study at hand, and post-hoc counts of interactions and co-occurrences. Using only the observed data, it is impossible to separate the three levels of uncertainty and our model does not aim to do so (as stated in lines 159-167 and lines 199-201). We therefore do not believe that an in-depth discussion of identifiability would add much value to the manuscript and, in the interest of space, have decided not to include one. Instead, we refer interested readers to~\citet{Weinstein2017} which does attempt to separate sources of uncertainty.

		Lines 159-167:

		\begin{quotation}
			When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij}=0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig. 1). Unfortunately, this is not possible for most interactions (except those where we know an interaction is truly not feasible). That is, we generally do not know \emph{why} an interaction was not observed, only that it was not. An empirical ecologist will instead measure the marginal probability $P(L_{ij})=k_{ij}/n_{ij}$, where $k_{ij}$ is the number of observed interactions between species $i$ and $j$ and $n_{ij}$ the number of observed co-occurrences. Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?
		\end{quotation}

@@

		\begin{refquote}
		1.      The simplest – do a better job of acknowledging what else has been done in the field – much of which has actually been done by the authors and their collaborators.  Given that they know there work I won't point that out (but they are under-siting this literature a bit) but they could consider Graham and Weinstein on-line early 2018 (I realise that this was just out when the author's submitted but it has some very similar messages) and the empirical example of Weinstein and Graham in Ecology letters 2017.  I don't think this would in any way diminish the importance of the current paper because I think the challenge in network ecology is to get people to use better quantitative methods.
		\end{refquote}

		\textbf{R:} We thank the Reviewer for stressing the need to further acknowledge previous work in the field. As this was also emphasised by other reviewers, we have taken this carefully \emph{ad notam} and expanded our references to earlier work as much as possible given length restrictions. We have taken particular care to add references to Graham/Weinsten papers as two of the reviewers suggested work by these authors. We hope that the introduction now presents a more thorough sample of previous work, remembering that our manuscript is not intended to be a comprehensive review.

		\begin{refquote}
		Line 7.  It is certainly true that most networks are snapshots in time but there is a growing realisation – including some nice examples (including those by the authors) that address this issue.  Maybe what you want to say is that we know that networks should not be considered static but we lack the tools – or ability to collect data – or whatever you think is the cause – to correct this situation. 
		\end{refquote}

		\textbf{R:} When revising the manuscript we removed line 7 and no longer refer to networks as snapshots.

@@

		\begin{refquote}
		3.      The set up (introduction) to the case study is quite odd and somehow seems off topic – or at least not logical based on what the reader has read up to that point.
		\medskip
		Line 240.  I found the justification for the system a bit odd.  Is the goal to show the gaps in sampling or to apply the model described thus far to consider the 3 different types of uncertainty outlined?  At this point the reader is confused about the goal...
		\medskip
		Line 249.  The statement about training data is redundant with what is stated above – adjust writing.
		\end{refquote}

		\textbf{R:} We have expanded our introduction of the case study (beginning line 295) to make it clear that we are using the highest-quality empirical network we can find as even such networks have uncertainty about unobserved interactions. This relates back to our point that urging increased sampling effort is not likely to solve problems of uncertainty as long as sampling is limited in the number of methodologies that can be applied, biased towards abundant or easy-to-identify species, restricted to particular spatial sites and/or environmental conditions (if the network is intended to be more general), or all of the above. Given budgetary constraints, it is extremely likely that empirical ecologists cannot sample as intensively and extensively as they would like and therefore some uncertainty is likely to remain. We repeat this point in the discussion to ensure that the case study is relevant. We have also clarified our statement that a strict application of Bayesian statistics does not allow empirical priors, but that they are an option for researchers that are more concerned about matching their prior to their study system than with strict formalism (lines 296-293). As Reviewer 1 points out, this is somewhat controversial and we feel it is important to note the potential objection.

		\begin{quotation}
		  \subsection*{An empirical example}

		      To illustrate the process of constructing a Bayesian network to quantify uncertainty about interactions, we use the comprehensively-sampled system of willows (\emph{Salix}), herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}. This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S5} for details). 
		      The high spatiotemporal resolution of this dataset make it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, there were many pairs of species which were rarely or never observed together and about which we therefore have high uncertainty about interaction probabilities (Fig. 2). Using the Bayesian framework above, we can identify which potential interactions are more and less uncertain, allowing us to better predict the true structure of the metaweb. 
		      % To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions. 
		      We calculated an empirical prior and computed the posterior distribution of the probability of an as-yet-unobserved interaction being feasible ($\lambda_{ij}$). We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for brevity, present only the latter here (see~\emph{Appendix S6} for \emph{Salix}-galler results).
		\end{quotation}

@@

		\textbf{R:} We have rephrased the manuscript and the word ``inevitable'' no longer appears. We hope that the current phrasing is less repetitive.

	7. Why not always model probabilities of co-occurrence?

		\begin{refquote}
		Line 142.  But shouldn't you model the probability of two species co-occurring?  The authors have a paper doing this.... Is that not a good idea?
		\end{refquote}

		\textbf{R:} Modelling the probability of co-occurrence is an option for many systems (e.g., aquatic food webs where ranges of fish species are fairly well-known, as in~\citet{Gravel2013}). It may also be possible to separate the probability of observing an interaction at a particular location into a metaweb component (the focus of the current manuscript) and a co-occurrence probability, as in~\citep{Gravel2018}. This addresses the question of interaction probabilities at specific locations, however, in contrast to our focus on metaweb interaction probabilities.

		In some systems, however, the factors affecting probabilities of co-occurrence may not be known. We therefore cannot suggest modelling co-occurrence as a panacea. Instead, we now emphasise that co-occurrence probabilities are one thing that could be included in a prior (section beginning line 231).

@@

		\textbf{R:} The redundant line has been removed. Thank you for pointing this out.

	10. Unsure about the point of filtering networks

		\begin{refquote}
		Line 295 to 302.  I would think that this second step (i.e., filtered networks) is to explore sampling not to determine how networks will be influenced by uncertainty?  Do you need the filtering step to evaluate uncertainty (as written it seems that this is the case)?
		\end{refquote}

		\textbf{R:} The filtering was intended to show how uncertainty likely warps our current understanding of network properties like connectance. If we do not observe 20-50\% of the interactions in a network, then many network properties in the published literature will be inaccurate. Even worse, networks compiled under different levels of uncertainty (e.g., species with more or less variable traits, or studies with multiple sampling methods versus only one) or with different sampling efforts will have network structure metrics that are inaccurate to different degrees. Filtering networks in the way that we do could give an idea of how many networks are missing, but we do not think it is necessary to evaluate uncertainty (we believe that examining the posterior distributions directly is a better approach there). Due to length restrictions, we have moved this analysis to an appendix (\emph{Appendix S10}) and have rephrased these lines to emphasise that the filtered networks are intended to demonstrate the consequences of uncertainty more than anything else.

@@

		\textbf{R:} The point of our method is not actually to quantify the amount of sampling needed. Although the ideal sampling effort \emph{can} be calculated using the framework we put forward (as we demonstrate), the real point is to quantify how uncertain we are that an interaction we do not observe really does not occur. Given this, we do not think that recommending uncertainty be explicitly stated undermines our point.

		The Reviewer's suggestion that we might need fewer samples for species that are ``specialised or bound to interact for some other reason'' reflects a very strong prior. In this case, yes we would need fewer samples for the species concerned. With sufficiently strong priors, it is not necessary to sample at all! For example, in most food webs it is assumed that basal resources will never consume prey even if a given resource and a given animal are never observed co-occurring and it is generally accepted that there is very low uncertainty about these zeros. In many cases, the assumptions involved in excluding interactions are less clear-cut and different researchers may disagree about which species are ``bound to interact'' (or not to interact). The concept of pollination syndromes is one example - many flower visitors are less rigidly specialised on particular flower types than initially thought~\citep{Ollerton2009}. To address such ``forbidden links``, we now suggest that researchers explicitly state both the uncertainty about data-based zeros and the assumptions by which they create structural zeros. This will allow future researchers to evaluate the uncertainty about all interactions in a network as the state of expert knowledge changes. We hope that this expanded recommendation (lines XX-XX) is clearer.

		Finally, we emphasise that the estimate of 30-50 samples does not refer to the \emph{Salix}-galler-natural enemy test system but to a much more general interpretation of the problem. Without a prior distribution and with \emph{no prior information}, as long as we assume that interaction probabilities follow a beta distribution it will take 30-50 observations of two species co-occurring to be 95-99\% confident that the species do not interact. Sampling requirements will be much less if an interaction was observed (note that in the empirical example we assume an interaction was feasible if it was observed even once).

@@

		\textbf{R:} As stated above, we do not agree that weighted networks reduce sampling biases. Moreover, we disagree that it is rare to use binary networks as most food webs (for example) are still binary. It takes an even greater sampling effort to quantify interaction strengths than the presence and absence of links, so for species-rich systems in particular there simply are not many high-quality weighted networks published. Moreover, as the Reviewer mentioned, empirical ecologists may already struggle to apply a Bayesian framework using qualitative data. We therefore opted not to extend our framework in this manuscript and leave this as an area for future work.

	5. Description of causes of uncertainty poorly integrated with the case study

		\begin{refquote}
		L50 This is a nice and clearly explained description of the problem that many network ecologists ignore, or are unaware of.
		Section from L50. This section is valuable, but had very weak links with the empirical analysis later in the paper. For instance in the example of the gall-formers, there was not formal discussion about the different sources of uncertainty. 
		\end{refquote}

		\textbf{R:} As we state in the section \textbf{Estimating uncertainty}, we usually cannot distinguish different sources of uncertainty in empirical data. Those studies which attempt to do so (e.g.,~\citet{Graham2018}) remove process uncertainty by assuming constant interaction probabilities during a short, intense sampling period and also assume that we know the true set of feasible interactions. This may be the case for Graham and Weinstein's relatively small and well-studied system but is not likely to be true for systems containing hundreds of species, systems containing recently-arrived species, systems just beginning to be studied, etc. A more generally-applicable approach is to test explicitly whether species always interact when co-occurring, whether interaction probability depends on the probability of co-occurrence, and whether both co-occurrence and interaction probabilities depend upon environmental conditions, as in~\citet{Gravel2018}. Note, however, that this study refers to the probability of an interaction occurring in a local realisation of a food web while we are concerned with metawebs in the present study.

@@

		To make this clearer, we have rephrased this section and added a line (lines 61-68) stating that we usually cannot determine the cause of all the zeros in an interaction matrix (we can identify obviously unfeasible interactions, but likely cannot say whether a zero for a rare species is because we did not observe enough individuals, there were not enough individuals to perform a particular interaction, or because the interaction is actually unfeasible). We hope that this revision makes it clearer that the description of different sources of uncertainty is a conceptual guide only.

		\begin{quotation}
			While an observed link definitely occurred (assuming correct identification of the species involved), a given link may not be observed for many reasons, \emph{whether or not it truly occurred} (Fig. 1). Moreover, given an unobserved interaction in an empirical dataset, we often cannot determine why the interaction was not observed \emph{post hoc}. The detection of any interaction is a stochastic process subject to many levels of uncertainty. As a conceptual guide, we describe three nested levels of uncertainty that roughly address the questions: ``Could species $i$ and $j$ interact?", ``Did they interact during sampling?", and ``Did we observe the interaction?"
		\end{quotation}

@@

	6. Process uncertainty poorly defined.

		\begin{refquote}
		L76ff `Process uncertainty' is not defined. The simplistic example of interaction uncertainty (fish eating a cactus) does not help the reader understand the detail of what is meant by `interaction uncertainty'. The two examples of `local constraints' (weather and habitat) are operating on completely different temporal scales (note – it is defined differently in L109). I would regard the issue of weather as much closer to detection uncertainty (e.g. for a pollinator, it would be likely to be interacting if the weather was better), whereas the issue of habitat is closer to the authors' `interaction uncertainty' (the species don't interact because they are not, or never, co-occurring in a habitat). Also if the species occur in different habitats then with an appropriate spatial scale of sampling then they do not co-occur – so the issue seems redundant. I suspect that the authors are thinking of a meta- or master network in much of their study, but this is not clear (or I have misunderstood and it needs to be explained better), i.e. the predicted presence of an interaction is not the presence of an interaction at the local site (taking detection and process uncertainty into account) but the ability to assess `interaction uncertainty'.
		\end{refquote}

### 2019-01-16 manuscript/CI_interactions.tex
integrated Dom's first-half comments to main text, need to reduce word count again

    First, ecological communities are stochastic~\citep{Gotelli2000}. Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilities and hence interactions~\citep{Vazquez2005,Poisot2015,Graham2018}. Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2013,Graham2018}. Even assuming constant co-occurrence within a system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010,Jordano2016}. Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Olesen2011a,Lopez2017}, between individuals~\citep{Pires2011a,Wells2013,Fodrie2015,Novak2015}, throughout life cycles~\citep{Clegg2018}, and with environmental conditions~\citep{Poisot2015}.

@@

    To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2013}) or very system-specific (e.g.,~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}); in either case such a model may be a poor fit for a particular study system. Moreover, some of the models described above cannot accommodate species observed only once~\citep{Bartomeus2013,Weinstein2017}. As rare species are likely to be observed less frequently~\citep{Bluthgen2006} and may be of particular interest (e.g., when modelling species loss), there is a need for a more widely-applicable framework that includes rarely-observed species.

    Here we introduce a simple, adaptable Bayesian framework. First, we briefly describe the nested levels of uncertainty affecting ecological network construction. In the context of this uncertainty, which can be reduced but not eliminated by high-quality sampling~\citep{Bartomeus2013}), we present a Bayesian framework which combines observed data with a prior expectation of network structure. We conclude with a worked example applying this framework to an intensively-sampled host-parasitoid network. We find that even the highest-quality empirical network data we could find had substantial uncertainty about whether many pairs of species interact, demonstrating the need to include information about this uncertainty in published networks. 
    % We also show that this interaction-level uncertainty leads to uncertainty about estimates of network structure, with important implications for comparisons across networks; especially those compiled with different sampling intensity~\citep{Weinstein2017}.

@@

          Fundamentally, some interactions are feasible while others are not~\citep{Poisot2015}. An unobserved interaction may have $\lambda_{ij}>0$, and the associated zero in an interaction matrix might be false. This uncertainty is partly addressed by trait-matching models~\citep{Bartomeus2016,Jordano2016,Weinstein2017}. Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L_{ij}$ between species $i$ and $j$, given some function describing trait matching $\mathbf{T_{ij}}$, as $P(L_{ij}|\mathbf{T_{ij}})=\lambda_{ij}$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}. In some cases the traits prohibiting an interaction are known and there will be little uncertainty about $\lambda_{ij}$. Generally, however, the traits that might prohibit an interaction are unknown~\citep{Dormann2017} and uncertainty about $\lambda_{ij}$ will be high. 
          %Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{Weinstein2017a} and herbivores may consume animal prey when it becomes accessible~\citep{Furness1988,Pietz2000}. These examples illustrate the danger in assuming that seemingly unlikely interactions cannot occur.
          As trait-matching models improve, uncertainty will be reduced~\citep{Jordano2016} and $\lambda_{ij}$ should either tend to 0 or to 1. Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}. This leaves some uncertainty about whether some species pairs could interact.

@@

            Both whether species can ever interact and whether they interact at a particular place and time have been discussed in the context of ``forbidden links"~\citep{Jordano2016}. In this framework, all links which are prevented by spatio-temporal uncoupling, physiological constraints, etc. are considered "structural zeros" that cannot be observed~\citep{Jordano1987,Jordano2016}. We conceptually distinguish between physiological constraints and spatio-temporal uncoupling to allow for cases in which a species is introduced to a new habitat, expands its range, or shifts phenology~\citep{Gravel2013}. In such cases, links which are impossible due to physiological constraints remain forbidden but links previously ``forbidden" by spatio-temporal mismatch could potentially occur.

@@

          Lastly, measurement errors are a pervasive source of uncertainty about ecological processes. Even an interaction which is feasible and occurs during sampling ($L_{ij}=1$, $X_{ij}=1$), may still go undetected~\citep{Jordano2016,Weinstein2017}. We can define the probability of detecting of an interaction, $D_{ij}$, given the interaction is feasible and occurs, as a stochastic process with  probability $P(D_{ij}|X_{ij}=1,L_{ij}=1)=\delta_{ij}$. Detection failure could happen for many reasons (see~\citet{Wirta2014}). Some sources of detection error can be minimised with appropriate sampling (e.g., combining multiple sampling methods~\citet{Wirta2014,Frost2016,Jordano2016}), but other sources are difficult to reduce. For example, it may not be possible to sample some species due to conservation concerns~\citep{Lagrue2015}. The probability of detecting an interaction will also depend on the duration of the interaction and its evidence, the species involved, and the individuals sampled~\citep{Wells2013,Lagrue2015,Cirtwill2016,Weinstein2017}. With improved sampling, $D_{ij}$ should tend towards 1 but, importantly $D_{ij}$ will vary between interactions and it is likely that $D_{ij}<1$ within a sample. For example, when detecting interactions based on gut contents interactions with slowly-digested prey with hard parts will be more detectable than interactions with quickly-digested, soft prey.

@@

    To sum up, the absence of an interaction could be because it was not feasible [$P(L_{ij})=0$], was feasible but did not occur during sampling ($P(X_{ij}|L_{ij}=1)=0$], or was feasible and occurred during sampling but could not be observed [$P(D_{ij}|X_{ij}=1,L_{ij}=1)=0$]. Note that some external factors can affect more than one level of uncertainty. For example, rare species are less likely to interact at a given site due to neutral processes~\citep{Jordano2016,Graham2018}. Interactions involving rare species are also less likely to be detected, unless more sampling effort is focused on rare than common species~\citep{Bartomeus2013,Jordano2016}. Thus, abundance affects both the probability of an interaction occurring at a particular site \emph{and} our ability to observe the interaction.

    When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij}=0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.~\ref{conceptual_fig}). Unfortunately, this is impossible for most interactions (unless we know an interaction is truly not feasible). That is, we generally do not know \emph{why} an interaction was not observed, only that it was not. An empirical ecologist will instead measure the marginal probability $P(L_{ij})=k_{ij}/n_{ij}$, where $k_{ij}$ is the number of observed interactions between species $i$ and $j$ and $n_{ij}$ the number of observed co-occurrences. Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?

@@

    The basis of a Bayesian approach to modelling the probability that an interaction between species $i$ and $j$ occurs ($\lambda_{ij}$) is combining the maximum likelihood estimate (MLE) of $\lambda_{ij}$ with a prior distribution (described in the next section) and a normalising function. The MLE of $\lambda_{ij}$ can be modelled as a Bernoulli trial based on the number of observed interactions $k_ij$ and observed co-occurrences $n_{ij}$: $\lambda_{ij}=\frac{k_{ij}}{n_{ij}}$. The most appropriate prior distribution for $\lambda_{ij}$ is the beta distribution:

@@

    Combining the prior distribution with the MLE of $\lambda_{ij}$ derived from observed data, we obtain a posterior distribution that also follows a beta distribution with new hyperparameters $\alpha_{ij}'=\alpha_{ij}+k$ and $\beta_{ij}'=\beta_{ij}+n-k$ (\emph{Appendix S3}). These definitions illustrate the influence of the prior on the posterior distribution: the difference between the posterior and the prior will increase with $k_{ij}$ and $n_{ij}-k_{ij}$. In other words, the distribution of $\lambda_{ij}$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and more on the observed data. As $n_{ij}$ increases, the total uncertainty about $\lambda_{ij}$ will decrease (Fig.~\ref{Salix_pdfs_cdfs}). Note that these models of $\lambda_{ij}$ do not distinguish between sources of uncertainty except through the choice of prior. For a model which attempts to separate sources of uncertainty, see~\citet{Weinstein2017}.

@@

      The choice of prior reflects a study's goal, the amount of prior knowledge available, and the strength of researchers' belief in that knowledge. Note that there is no 'correct' prior as long as the true distribution of interaction probabilities is unknown~\citep{Spiegelhalter2000}. The goal is to select a reasonable prior that reflects our assumptions about the true distribution and then adjust this prior with observed data as it becomes available. When in doubt, it is also possible to model interaction probabilities using a variety of priors and compare results~\citep{Spiegelhalter2000}.

      Some researchers are reluctant to adopt a Bayesian approach because of its perceived subjectivity (i.e., a metaweb simulated using a Bayesian distribution will depend upon the assumptions inherent in the prior). We argue that one of the advantages of the Bayesian approach is that it makes this subjectivity explicit~\citep{Spiegelhalter2000}. Researchers compiling empirical networks face many decisions about where to set community boundaries, the set of species to include in the focal community~\citep{Jordano2016}, what type of sampling is most appropriate~\citep{Wirta2014}, etc. These choices all affect the compiled network and most do not have clear answers, making all empirical networks (and all theoretical networks, which likewise depend upon the assumptions used in building the network) somewhat subjective. In addition, researchers distinguishing ``forbidden links" inherently rely on prior knowledge to identify these links~\citep{Jordano2016}. Stating that an interaction is ``forbidden" is, in effect, applying a very strong prior to reduce/eliminate uncertainty about the non-observation of that interaction. Given the reality of subjective network construction, we feel it is better to make the assumptions used to build a network as explicit as possible so that these assumptions can be questioned, compared between studies, tested, and perhaps validated.

@@

        Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact. The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact. We calculated the number of samples required to reach 95\% confidence that $\lambda_{ij}$ was below thresholds of 0.1, 0.05, and 0.01 as examples (see function ``samples\_for\_threshold";~\emph{Appendix S9}). Finally, we may be interested in measures of network structure rather than the network itself. We can use the posterior distributions of interactions to generate a suite of plausible ``true'' networks that would be obtained if sampling uncertainty could be eliminated and use these networks to estimate many network properties (see \emph{Appendix S10} for a worked example).

>>>>

    First, ecological communities are stochastic~\citep{Gotelli2000}. Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilities and hence interactions~\citep{Vazquez2005,Poisot2015,Graham2018}. Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2018,Graham2018}. Even assuming constant co-occurrence within a system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010,Jordano2016}. Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Olesen2011a,Lopez2017}, between individuals~\citep{Pires2011a,Wells2013,Fodrie2015,Novak2015}, throughout life cycles~\citep{Clegg2018}, and with environmental conditions~\citep{Poisot2015}.

@@

    To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2018}) or very system-specific (e.g.,~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}); in either case such a model may be a poor fit for a particular study system. Moreover, some of the models described above cannot accommodate species observed only once~\citep{Bartomeus2013,Weinstein2017}. As rare species are likely to be observed less frequently~\citep{Bluthgen2006} and may be of particular interest (e.g., when modelling species loss), there is a need for a more widely-applicable framework that includes rarely-observed species.

    Here we introduce a simple, adaptable Bayesian framework. First, we briefly describe the nested levels of uncertainty affecting ecological network construction. Understanding this nesting is an important step towards formalising our interpretation of the different drivers of uncertainty about interactions. Importantly, we distinguish between the possibility that an interaction is unfeasible (cannot occur) and the possibility that, given an interaction is feasible, it may not occur during a particular sampling event.

    In the context of this uncertainty, which can be reduced but not eliminated by high-quality sampling~\citep{Bartomeus2013}), we present a Bayesian framework which combines observed data with a prior expectation of interaction probabilities. We conclude with a worked example applying this framework to an intensively-sampled host-parasitoid network. We find that even the highest-quality empirical network data we could find has substantial uncertainty about whether many pairs of species interact, demonstrating the need to include information about this uncertainty in published networks. 
    % We also show that this interaction-level uncertainty leads to uncertainty about estimates of network structure, with important implications for comparisons across networks; especially those compiled with different sampling intensity~\citep{Pelissier2017,Tylianakis2017,Weinstein2017}.

@@

          Fundamentally, some interactions are feasible while others are not~\citep{Poisot2015}. An unobserved interaction may have $\lambda_{ij}>0$, and the associated zero in an interaction matrix might be false. This uncertainty is partly addressed by trait-matching models~\citep{Bartomeus2016,Jordano2016,Weinstein2017}. Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L_{ij}$ between species $i$ and $j$ given some function describing trait matching $\mathbf{T_{ij}}$ as $P(L_{ij}|\mathbf{T_{ij}})=\lambda_{ij}$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}. In some cases the traits prohibiting an interaction are known and there will be little uncertainty about $\lambda_{ij}$. Generally, however, the traits that might prohibit an interaction are unknown~\citep{Dormann2017} and uncertainty about $\lambda_{ij}$ will be high. 
          %Pollinators may visit plants outside of those predicted based on ``pollination syndromes"~\citep{Weinstein2017a} and herbivores may consume animal prey when it becomes accessible~\citep{Furness1988,Pietz2000}. These examples illustrate the danger in assuming that seemingly unlikely interactions cannot occur.
          As trait-matching models improve, uncertainty will be reduced~\citep{Jordano2016} and $\lambda_{ij}$ should either tend to 0 or to 1. Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}. This leaves some uncertainty about whether some species pairs could interact.

@@

            Both whether species can ever interact and whether they interact at a particular place and time have been discussed in the context of ``forbidden links"~\citep{Jordano2016}. In this framework, all links which are prevented by spatio-temporal uncoupling, physiological constraints, etc. are considered ``structural zeros" that cannot be observed~\citep{Jordano1987,Jordano2016}. We conceptually distinguish between physiological constraints and spatio-temporal uncoupling to allow for cases in which a species is introduced to a new habitat, expands its range, or shifts phenology~\citep{Gravel2013}. In such cases, links which are impossible due to physiological constraints remain forbidden but links previously ``forbidden" by spatio-temporal mismatch could potentially occur. When considering local realisations of a metaweb, it is possible to distinguish between interactions forbidden by traits and those forbidden by lack of co-occurrence~\citep{Gravel2018}. In the present study, we are concerned with identifying the metaweb-- the set of interactions which are feasible assuming species co-occur.

@@

          Lastly, measurement errors are a pervasive source of uncertainty about ecological processes. Even an interaction which is feasible and occurs during sampling ($L_{ij}=1$, $X_{ij}=1$), may still go undetected~\citep{Jordano2016,Weinstein2017}. We can define the probability of detecting of an interaction, $D_{ij}$, given the interaction is feasible and occurs, as a stochastic process with  probability $P(D_{ij}|X_{ij}=1,L_{ij}=1)=\delta_{ij}$. Note that $D_{ij}$ is a stochastic variable taking the variable 1 if observed and 0 otherwise, while $P(D_{ij})$ is the probability that $D_{ij}=1$. Detection failure could happen for many reasons (see~\citet{Wirta2014}). Some sources of detection error can be minimised with appropriate sampling (e.g., combining multiple sampling methods~\citet{Wirta2014,Frost2016,Jordano2016}), but other sources are difficult to reduce. For example, it may not be possible to sample some species due to conservation concerns~\citep{Lagrue2015}. The probability of detecting an interaction will also depend on the duration of the interaction and its evidence, the species involved, and the individuals sampled~\citep{Wells2013,Lagrue2015,Cirtwill2016,Weinstein2017}. With improved sampling, $D_{ij}$ should tend towards 1 but, importantly $D_{ij}$ will vary between interactions and it is likely that $D_{ij}<1$ within a sample. For example, when detecting interactions based on gut contents interactions with slowly-digested prey with hard parts will be more detectable than interactions with quickly-digested, soft prey.

@@

    To sum up, the absence of an interaction could be because it was not feasible [$P(L_{ij})=0$], was feasible but did not occur during sampling ($P(X_{ij}|L_{ij}=1)=0$], or was feasible and occurred during sampling but could not be observed [$P(D_{ij}|X_{ij}=1,L_{ij}=1)=0$]. Researchers might be interested in whether an un-recorded interaction is feasible (i.e., reducing uncertainty about $\lambda_{ij}$) or whether or not a feasible interaction occurred locally (i.e., reducing uncertainty about $\chi_{ij}$). Here we consider the former, while noting that uncertainty about both $\chi_{ij}$ and $\delta_{ij}$ contribute to uncertainty about $\lambda_{ij}$. Future sampling should aim to characterise all three probabilities, but for now it is often difficult to distinguish between them. One reason for this is the ability of external factors such as abundance to affect multiple levels of uncertainty. Rare species are less likely to interact at a given site due to neutral processes~\citep{Jordano2016,Graham2018} and interactions involving rare species are less likely to be detected~\citep{Bartomeus2013,Jordano2016}. Thus, abundance affects both $P(X_{ij})$ and $P(D_{ij})$.

    When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij}=0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.~\ref{conceptual_fig}). Unfortunately, unlike studies focused on local realisations of a network (e.g.,~\citet{Graham2018,Gravel2018}), in a metaweb we generally do not know \emph{why} an interaction was not observed. An empirical ecologist will measure the marginal probability $P(L_{ij})=k_{ij}/n_{ij}$, where $k_{ij}$ is the number of observed interactions between species $i$ and $j$ and $n_{ij}$ the number of observed co-occurrences. Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?

@@

    The basis of a Bayesian approach to modelling the probability that an interaction between species $i$ and $j$ occurs ($\lambda_{ij}$) is combining the maximum likelihood estimate (MLE) of $\lambda_{ij}$ with a prior distribution (described in the next section) and a normalising function. The MLE of $\lambda_{ij}$ can be computed from the number of observed interactions $k_ij$ and observed co-occurrences $n_{ij}$: $\lambda_{ij}=\frac{k_{ij}}{n_{ij}}$. The most appropriate prior distribution for $\lambda_{ij}$ is the beta distribution:

@@

    Combining the prior distribution with the MLE of $\lambda_{ij}$ derived from observed data, we obtain a posterior distribution of $\lambda_{ij}$ that also follows a beta distribution with new hyperparameters $\alpha_{ij}'=\alpha_{ij}+k$ and $\beta_{ij}'=\beta_{ij}+n-k$ (\emph{Appendix S3}). These definitions illustrate the influence of the prior on the posterior distribution: the difference between the posterior and the prior will increase with $k_{ij}$ and $n_{ij}-k_{ij}$. In other words, the distribution of $\lambda_{ij}$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and more on the observed data. As $n_{ij}$ increases, the total uncertainty about $\lambda_{ij}$ will decrease (Fig.~\ref{Salix_pdfs_cdfs}). Note that these models of $\lambda_{ij}$ are designed to i) quantify and ii) reduce the total uncertainty about $\lambda_{ij}$. They do not distinguish between sources of uncertainty except through the choice of prior.

@@

      The choice of prior reflects a study's goal, the amount of prior knowledge available, and the strength of researchers' belief in that knowledge. Note that there is no 'correct' prior as long as the true distribution of interaction probabilities is unknown~\citep{Spiegelhalter2000}. The goal is to select a reasonable prior that reflects our assumptions about the true distribution and then adjust it with observed data as it becomes available. When in doubt, it is also possible to model interaction probabilities using a variety of priors and compare results~\citep{Spiegelhalter2000}.

      Some researchers are reluctant to adopt a Bayesian approach because of its perceived subjectivity (i.e., a metaweb simulated using a Bayesian distribution will depend upon the assumptions inherent in the prior). We argue that one of the advantages of the Bayesian approach is that it makes this subjectivity explicit~\citep{Spiegelhalter2000}. Researchers compiling empirical networks face many decisions about where to set community boundaries, the set of species to include in the focal community~\citep{Jordano2016}, what type of sampling is most appropriate~\citep{Wirta2014}, etc. These choices all affect the compiled network and most do not have clear answers, making all empirical networks (and all theoretical networks, which likewise depend upon the assumptions used in building the network) somewhat subjective. In addition, researchers distinguishing ``forbidden links" inherently rely on prior knowledge to identify these links~\citep{Jordano2016}. Stating that an interaction is ``forbidden" is, in effect, applying a very strong prior to reduce/eliminate uncertainty about the non-observation of that interaction. This is especially true when researchers assume that any species not observed co-occurring could not ever interact. Given the reality of subjective network construction, we feel it is better to make the assumptions used to build a network as explicit as possible so that these assumptions can be questioned, compared between studies, tested, and perhaps validated.

@@

        Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many observations are necessary to be confident that two co-occurring species do not interact (note that the beta distribution can never equal 0 or 1). The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact. We calculated the number of samples required to reach 95\% confidence that $\lambda_{ij}$ was below thresholds of 0.1, 0.05, and 0.01 as examples (see function ``samples\_for\_threshold";~\emph{Appendix S9}). Finally, we may be interested in measures of network structure rather than the network itself. We can use the posterior distributions of interactions to generate a suite of plausible ``true'' networks that would be obtained if sampling uncertainty could be eliminated and use these networks to estimate many network properties (see \emph{Appendix S10} for a worked example).
